LogChunks: A Data Set for Build Log Analysis

### 2020-01-15 msr-paper/paper.tex
Done until L280

\usepackage{listings}
\usepackage{tabularx}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software engineering~\cite{hilton2016usage}.
Many software projects use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
CI builds produce logs which report the results of the steps within the build.
These build logs contain a lot of valuable information for developers and researchers, for example:
%Developers examine time measurement log statements to track how different stages of the build process perform.
%Researchers collect the commands triggering the build steps to reverse engineer the build configuration when only the log is available to them.
descriptions of compile errors, linter warnings or failed tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

However, build logs are verbose and
long~\cite{beller2017oops}---sometimes in excess of 50 MB of ASCII
text for one build---, making them inadequate for direct consumption.
Therefore, developers and researchers can only efficiently use the
information within the build logs if we can at least
semi-automatically retrieve the chunks of the log that describe the
targeted information.

@@

Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks is
  openly available on Zenodo: \todo{insert zenodo link}} a collection
of 797 Travis CI build logs from 80 GitHub repositories spread over 29
programming languages.  For each build log, we manually labeled chunk
describing why the build failed.  The data set also provides keywords
the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

%\subsection{Potential Use Cases}
\emph{LogChunks} can be the basis for a wide range of further studies:

\section{Related Data Sets}
\label{sec:related-data-sets}
This section presents existing data sets of CI build logs and how
\emph{LogChunks} is different from them.

\subsection{TravisTorrent}
\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
range of metadata about builds on Travis CI\@.  It combines data
accessible through the public Travis CI and GitHub APIs and through
GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
metadata are the failing test cases.  However, TravisTorrent obtained
these through a manually developed parser, which only supports
specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
many of the failing tests are at least incomplete and lack
validation. By contrast, \emph{LogChunks} provides manually labeled
data on the description of why builds failed for a much wider
selection of build tools.

This section presents the file structure and the data schema of \emph{LogChunks}.
%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
The build logs are organized in folders for each language and repository.
Within each repository folder, folders for each build status contain the log files named with the corresponding build ID.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.

The folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
The data set provides an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
Listing~\ref{lst:examples} presents the schema of these XML files.

For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
Figure \ref{tab:data-in-example} presents the data within each example.
% Each \texttt{Example} consists of:
% \begin{itemize}
% 	\item \texttt{Log:} the relative path to the input build log.
% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
% 				The category is relative to the other examples for the same repository.
% \end{itemize}
Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build logs that describes why the build failed.
This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
When the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes the description \emph{that} the build failed.
%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
%In these instances the \texttt{Chunk} contains the lines describing that the build failed.

\section{Data Collection Process}
This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
\label{sec:data-collection}

\subsection{Log Collection}
We describe how we select the repositories, builds and logs for \emph{LogChunks}.
To collect the build logs we built the \texttt{GHTorrentParser} and \texttt{TravisRequester} using Ruby.

\paragraph{Repository Sampling}
%First, we determine a set of repositories to query logs from.
Our \texttt{GHTorrentParser} queries the \emph{GHTorrent}~\cite{gousios2013ghtorrent} data set for the most popular languages on GitHub.
It then retrieves the most popular repositories for a given language.
We define \emph{Popularity} as the number of watches.
The \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, then checks whether a given repository uses Travis CI\@.

For \emph{LogChunks} we queried GHTorrent on 01/04/2018 for the three most popular repositories of each of the 30 most popular languages.
Among the resulting repositories are, for example, \texttt{git/git}, \texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\paragraph{Build Sampling}
The \texttt{TravisRequester} obtains the newest builds for a given repository.
We use a stratified sampling approach and save the obtained builds in buckets according to their status.
%We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.
The user of \texttt{TravisRequester} configures how many builds should be checked and how many builds per status should be saved.

@@

\paragraph{Log Sampling}
For each build, the \texttt{TravisRequester} then selects a log to download.
Travis CI links logs to \emph{jobs}.
A build can consist of multiple jobs, e.g.\ executing tests in different environments.
%A failed build can have successful job executions, as just one failed job leads to the whole build being marked as failed.
\texttt{TravisRequester} queries each build for the first job which has the same state and obtains the corresponding build log.

@@

@@

\paragraph{Include More Repositories and Logs}
\emph{LogChunks} encompasses a wide range of repositories from various main development languages, though only 10 logs from each repository.
%This stems from the high effort necessary for the manual data labeling process.
Including more logs and repositories into \emph{LogChunks} will strengthen it as a benchmark to compare build log analysis techniques.

>>>>

\usepackage{listings}
\usepackage{tabularx}
\usepackage{cleveref}

@@

\section{Introduction}
Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report the results of the steps within the build.  These build logs
contain a lot of valuable information for developers and researchers,
for example: descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

However, build logs can be verbose and large---sometimes in excess of
50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
for direct human consumption. Therefore, to support developers and
researchers in efficiently making use of the information within build
logs, we must at least semi-automatically retrieve the chunks of the
log that describe the targeted information.

@@

Thus, in this paper, we present \emph{LogChunks},\footnote{LogChunks
  is openly available on Zenodo: \todo{insert zenodo link}} a
collection of 797 Travis CI build logs from 80 GitHub repositories in
29 programming languages.  For each build log, we manually labeled
the chunk describing why the build failed.  The data set also provides
keywords the authors would use to search for the labeled log chunk and
categorizes the log chunks according to their format within the log.

\todo{mention most popular repositories very briefly somewhere?}
\todo{80x -> 80}
\begin{figure}[tbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

\section{Creating LogChunks}
This section presents how we gathered the logs for \emph{LogChunks} and our manual labeling process.
\label{sec:data-collection}

\subsection{Log Collection}
In this section, we describe how we created \emph{LogChunks} along the
overview in \Cref{fig:lc-overview}. All steps are automatized as Ruby
scripts\todo{link to repo?} and highly configurable.

\paragraph{Repository Sampling}
We first query \emph{GHTorrent}~\cite{gousios2013ghtorrent} for the
most popular languages on GitHub, and subsequently, the most popular
(by number of watchers) repositories for a given language. We measure
popularity by the number of watchers.  We only select repositories
which use Travis CI\@.

For \emph{LogChunks}, we queried GHTorrent on 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

\todo{we need some reasoning for most popular, our proxy for
  popularity (watchers) -- as is often done, reference --, and ideally, how much
  data we are including}

\paragraph{Build Sampling}
We use a sampling approach using the build status as our stratum.
\todo{What are our strata?}
%We encountered the following statuses during our data collection: created, started, cancelled, passed, errored and failed.

@@

\paragraph{Log Sampling}
Travis CI build comprise of a number of jobs that actualize a build
process in a defined environment. As such, the outcome from different
jobs might be different. For each build in LogChunks, we download the
first job which has the same state as the overall build.

@@

%\subsection{Potential Use Cases}
\emph{LogChunks} can be the basis for a range of further studies:

\section{Related Data Sets}
\label{sec:related-data-sets}
This section presents existing data sets of CI build logs and how
\emph{LogChunks} differs from them.

\subsection{TravisTorrent}
\emph{TravisTorrent}~\cite{beller2017travistorrent} collects a broad
range of metadata about Travis CI builds\@.  It combines data
accessible through the public Travis CI and GitHub APIs and through
GHTorrent~\cite{gousios2013ghtorrent}. Similar to LogChunks, among the
metadata are the failing test cases. However, TravisTorrent obtained
these through a manually developed parser, which only supports
specific Ruby test runners and Java Maven or JUnit logs. Anecdotally,
many of the failing tests are at least incomplete and lack
validation. By contrast, \emph{LogChunks} provides manually labeled
and two-fold cross-validated data of why builds failed, not only for
failing tests like TravisTorrent, but for all possible build-failing
errors.

This section presents the internal structure and data schema of
\emph{LogChunks}. In principle, LogChunks comprises automatically
retrieved and manually cross-validated data.

\subsection{Automatic data.}
%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
LogChunks comprises information on \todo{x} build logs, which are organized in folders for each language and repository.
Within a repository folder, there are folders for each of the general build status ('successful', 'failed', ...), which contain the entire unaltered log files.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.
For each repository, \emph{LogChunks} gives about 10 \texttt{Examples}.
Figure \ref{tab:data-in-example} presents the data within each example.

The top-level folder \texttt{build-failure-reason} contains the manually labeled data of \emph{LogChunks}.
The data set contains an XML file for each repository: \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater.xml}.
Listing~\ref{lst:examples} presents the schema of these XML files.

% Each \texttt{Example} consists of:
% \begin{itemize}
% 	\item \texttt{Log:} the relative path to the input build log.
% 	\item \texttt{Chunk:} the log chunk that describes why the build failed.
% 	\item \texttt{Keywords:} keywords the authors would use to search for the log chunk.
% 	\item \texttt{Category:} a categorization of the structural representation of the log chunk within the build log.
% 				The category is relative to the other examples for the same repository.
% \end{itemize}
Following, this section defines in more detail the labeled log chunk, search keywords and structural categories.

\paragraph{Chunk That Describes Why The Build Failed}
The \texttt{Chunk} is the substring of the build log that describes why the build failed.
This can, for example, be the failing test case or a compiler error and is one continuous substring of the build log.
In cases where the reason \emph{why} the build failed was described in an external log, the \texttt{Chunk} includes only the fact \emph{that} the build failed.
%Wherever possible, it does \emph{not} include the log statements describing \emph{that} the build failed, but the description of \emph{why} it failed.
%For a few logs we were unable to define the section detailing why the build failed, e.g.\ because this information was logged in another log file.
%In these instances the \texttt{Chunk} contains the lines describing that the build failed.

@@

\paragraph{Include More Repositories and Logs}
\emph{LogChunks} encompasses a range of repositories from various main development languages, though only 10 logs from each repository.
%This stems from the high effort necessary for the manual data labeling process.
Including more logs and repositories into \emph{LogChunks} will strengthen it as a benchmark to compare build log analysis techniques.
